Comparing vector-based and Bayesian memory models using large-scale datasets:\protect\\User-generated hashtag and tag prediction on Twitter and StackOverflow

### 2016-01-24 writeups/psycMethods/psycMethods.tex
foo

@@

\subsubsection{Addressing Word Order}

>>>>

As a general methodology for this research, we are using a cognitively-constrained exploratory model development process.
Since we are working with large-scale datasets, we have enough data to explore many different modifications simultaneously without the risk of overfitting.
However, we are not interested in bringing to bear the entire collection of machine learning algorithms to this prediction task in order to completely optimize a model.
Rather, we are interested in evaluating how well two cognitive models can explain the results, and then making selective modifications to them to see how performance changes.
The modifications that we explored were picked such that they influenced model accuracy, could be easily added to (or removed from) the cognitive models without massive modifications, and could be considered cognitively plausible.

@@

\subsubsection{Word Order for Vector-Based Systems}
